Incremental Faint Object Detection in Multi-Epoch Observations

### 2016-11-02 ms.tex
Title change; minor intro changes

\title{Faint Object Detection in Multi-Epoch Observations}
%\journalinfo{To appear in ApJ?}
\journalinfo{Submitted to Apj}

@@

We here address the second alternative, considering how best to use the list of detections while the observations are in progress to prune spurious source detections but keep the sources associated with genuine objects.

@@

\noindent 
To make the analysis analytically tractable and the results easy to interpret, we here restrict ourselves to an idealized setting; we will present a more general treatment in a subsequent paper.

>>>>

\title{Incremental Faint Object Detection in Multi-Epoch Observations}
%\journalinfo{To appear in ApJ?}
\journalinfo{Submitted to Apj}

@@

We here address the second alternative, considering how best to use the list of detections while the observations are in progress to prune spurious source detections but keep the sources associated with genuine objects.
The study presented here is exploratory, to establish the basic ideas and provide initial metrics for studying the feasibility of the incremental approach.
To make the analysis analytically tractable and the results easy to interpret, we restrict ourselves to an idealized setting; we will present a more general treatment in a subsequent paper.

@@

\noindent
